---
title: "Property Analysis of Ferroelastomer"
author: "Billy Koech"
date: "10/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# import libraries
library(tidyverse) # tidy
library(janitor) # for cleaning names
library(readxl) # package for importing data
```

## Permeability Analysis


```{r}

# load data

file_path <- "~/Google\ Drive/for_Billy_Koech/from_Billy/Fe+Elastomer\ experiments/V2_experiment_design_mixing_ratios_by_volume.xlsx"

ferroelastomer_data <- read_xlsx(file_path,
                                 sheet = 2,
                                 range = cell_rows(1:53)) %>%
                                 clean_names()



# gather the data
gathered_data <-ferroelastomer_data %>%
                gather(c(x1_inductance_u_h_at_1khz,
                         x2_inductance_u_h_at_1khz,
                         x3_inductance_u_h_at_1khz,
                         x4_inductance_u_h_at_1khz,
                         x5_inductance_u_h_at_1khz), 
                       key = "quantity",
                       value = "uH",
                       na.rm = FALSE)

# group byo sample number and compute mean and standard deviation
avg_and_std <- gathered_data %>%
                    group_by(sample_number, 
                             volume_ratio,
                             particle_size_microns,
                             mass_ratio, ecoflex,
                             vacuumed,
                             repeated) %>%
                    summarise(avg = mean(uH), dev = sd(uH))



# plot raw data:
# ggplot(gathered_data,aes(x = volume_ratio,
#                         y = uH,
#                         group = particle_size_microns,
#                         color = as.factor(particle_size_microns))) +
#      geom_line()

# grouped with average and sd on a single plot, grouped by particle_size_microns
# ggplot(avg_and_std, aes(x = volume_ratio,
#                         y = avg, 
#                         group = particle_size_microns, 
#                         color = as.factor(particle_size_microns))) +
#         geom_line() +
#         geom_point() +
#         labs(title = "Graph of Inductance against volume ratio",
#              subtitle  = "Each line represents particles of different sizes",
#              color = "Iron particle sizes") + 
#         xlab(label = "Percentage of Iron in sample by volume") + 
#         ylab(label = "Inductance measured at 1KHz") +
#         geom_errorbar(aes(ymin=avg-dev,
#                           ymax=avg+dev), width=.01)


# faceted by particle_size_microns
# ggplot(avg_and_std, aes(x = volume_ratio,
#                         y = avg)) + 
#         facet_wrap(~particle_size_microns) +
#         geom_line() +
#         geom_point() +
#         labs(title = "Graph of Inductance against volume ratio",
#              subtitle  = "Each box represents particles of different sizes",
#              color = "Iron particle sizes") + 
#         xlab(label = "Percentage of Iron in sample by volume") + 
#         ylab(label = "Inductance measured at 1KHz") +
#         geom_errorbar(aes(ymin=avg-dev,
#                           ymax=avg+dev), width=.01)


# graph of inductance versus mass ratio to 
# ggplot(avg_and_std,aes(x = mass_ratio,
#                        y = avg,
#                        group = particle_size_microns,
#                        color = as.factor(particle_size_microns))) +
#   geom_line() +
#   geom_point() +
#   labs(title = "Graph of Inductance against mass ratio",
#        subtitle  = "Each line represents particles of different sizes",
#        color = "Iron particle sizes") +
#   xlab(label = "Percentage of Iron in sample by mass") +
#   ylab(label = "Inductance measured at 1KHz") +
#   geom_errorbar(aes(ymin=avg-dev,
#                     ymax=avg+dev), width=.01)


# function to plot graph params:
# plot_by: name of column to use for x axis => volume_ratio or mass_ratio
# ecoflex_n : type of ecoflex
# vacuumed_bool: whether to plot vacuumed or non_vacuumed
# repeat_param: change to 1 to plot fialed values only
# apply_func: fuction to change values in y axis
# graph_name : goes on title and y axis label

plot_graph <- function(plot_by, ecoflex_n, vacuumed_bool, repeat_param=0, apply_func, graph_name){
  
  avg_and_std %>%
    filter(ecoflex == ecoflex_n,
           vacuumed == vacuumed_bool,
           repeated == repeat_param) %>% 
    ggplot(aes(x = eval(parse(text = plot_by)),
               y = apply_func(avg),
               group = particle_size_microns,
               color = as.factor(particle_size_microns))) +
    geom_line() +
    geom_point() +
    labs(title = paste("Graph of", graph_name, "against", plot_by, "for Ecoflex ", ecoflex_n),
         subtitle  = "Each line represents particles of different sizes",
         color = "Iron particle sizes") + 
    xlab(label = paste("Percentage of Iron in sample by ", plot_by)) + 
    ylab(label = graph_name) +
    geom_errorbar(aes(ymin= apply_func(avg-dev), ymax= apply_func(avg+dev)), width=.01) +
    geom_hline(yintercept = apply_func(412.7), color = "red") +
    geom_hline(yintercept = apply_func(1076.2), color = "blue")
  
}

# faceted plot
# same as plot_graph but makes facets instead
plot_graph_faceted <- function(plot_by, ecoflex_n, vacuumed_bool, repeat_param=0, apply_func, graph_name){
  
  avg_and_std %>%
    filter(ecoflex == ecoflex_n,
           vacuumed == vacuumed_bool,
           repeated == repeat_param) %>% 
    ggplot(aes(x = eval(parse(text = plot_by)),
               y = apply_func(avg),
               )) +
    facet_wrap(~particle_size_microns) +
    geom_line() +
    geom_point() +
    labs(title = paste("Graph of", graph_name, "against", plot_by, "for Ecoflex ", ecoflex_n),
         subtitle  = "Each box represents particles of different sizes",
         color = "Iron particle sizes") + 
    xlab(label = paste("Percentage of Iron in sample by ", plot_by)) + 
    ylab(label = graph_name) +
    geom_errorbar(aes(ymin= apply_func(avg-dev), ymax= apply_func(avg+dev)), width=.01) +
    geom_hline(yintercept = apply_func(412.7), color = "red") +
    geom_hline(yintercept = apply_func(1076.2), color = "blue")
  
}

L_to_miu_r <- function(L){
  l <- 6.23 * 10^(-3)       # lenght of coil in meters
  u_o <- 1.26 * 10^(-6)     # permeability of free space in T-m/At
  N <- 100                  # number of turns
  A <- pi * (5 * 10^(-3))^2 # cross sectional area of coil, radius = 5mm
    
  # calculate relative permeability
  return((L * (10^(-6)) * l) / (u_o * (N^2) * A))
}

# function that does not alter input
no_function <- function(input){
  return(input)
}

# ecoflex 30 graphs
plot_graph(plot_by = "volume_ratio", ecoflex_n = 30, vacuumed_bool = 0, repeat_param = 0, apply_func = L_to_miu_r, graph_name = "Relative Permeability")

plot_graph_faceted(plot_by = "volume_ratio", ecoflex_n = 30, vacuumed_bool = 0, repeat_param=0, apply_func = L_to_miu_r, graph_name = "Relative Permeability")

plot_permeability_faceted_by_volume(ecoflex_n = 30, vacuumed_bool = 0)
plot_permeability_graph_by_mass(ecoflex_n = 30, vacuumed_bool = 0)
plot_permeability_faceted_by_mass(ecoflex_n = 30, vacuumed_bool = 0)


# ecoflex 20 graphs
plot_permeability_graph_by_volume(ecoflex_n = 20, vacuumed_bool = 0)




# faceted plot
# same as plot_graph but makes facets instead
vacuum_comparison_graph <- function(plot_by, ecoflex_n, repeat_param=0, apply_func, graph_name){
  
  avg_and_std %>%
    filter(ecoflex == ecoflex_n,
           repeated == repeat_param,
           vacuumed != 2) %>% 
    ggplot(aes(x = eval(parse(text = plot_by)),
               y = apply_func(avg),
               group = vacuumed,
               color = as.factor(vacuumed))) +
    facet_wrap(~particle_size_microns) +
    geom_line() +
    geom_point() +
    labs(title = paste("Graph of", graph_name, "against", plot_by, "for Ecoflex ", ecoflex_n),
         subtitle  = "Each box represents particles of different sizes",
         color = "Vacuum state") + 
    xlab(label = paste("Percentage of Iron in sample by ", plot_by)) + 
    ylab(label = graph_name) +
    geom_errorbar(aes(ymin= apply_func(avg-dev), ymax= apply_func(avg+dev)), width=.01) +
    geom_hline(yintercept = apply_func(412.7), color = "red") +
    geom_hline(yintercept = apply_func(1076.2), color = "blue")
  
}
# function to plot permeability against volume ratio
particle_size_plot_permeability_graph_by_volume <- function(ecoflex_n, repeat_param = 0, size_p){
  
  avg_and_std %>%
    filter(ecoflex == ecoflex_n,
           repeated == repeat_param,
           particle_size_microns == size_p,
           vacuumed != 2) %>% 
    ggplot(aes(x = volume_ratio,
               y = avg,
               group = vacuumed,
               color = as.factor(vacuumed))) +
    geom_line() +
    geom_point() +
    labs(title = paste("Graph of Inductance against volume ratio for Ecoflex ", ecoflex_n),
         subtitle  = paste("Plot for vaccumed and Non vacuumed for", size_p, " micron particles"),
         color = "Vacuum state") + 
    xlab(label = "Percentage of Iron in sample by volume") + 
    ylab(label = "Inductance measured at 1KHz") +
    geom_errorbar(aes(ymin=avg-dev, ymax=avg+dev), width=.01) +
    geom_hline(yintercept = 412.7, color = "red") +
    geom_hline(yintercept = 1076.2, color = "blue")
  
}


# plot vacuumed samples and non vacuumed for particles size = 300
particle_size_plot_permeability_graph_by_volume(ecoflex_n=30, repeat_param = 0, size_p=300)
vacuum_comparison_graph(plot_by = "volume_ratio", ecoflex_n = 30, repeat_param=0, apply_func = L_to_miu_r, graph_name = "Relative permeability")

```

## Summary of the results

# Instructions:
One to two page report

* change inductance to permeability
* summarise the results
  * methodology
    * sample fabrication
    * material used
    * table of particles, ecoflex, curing time, mean, median, standard deviation,
    * measurement methods for the inductance
  * Graphs 
    * Graphs with volume ratio and inductance/ permeabiltiy (two scales on the y axis)
    * Graphs with volume ratio and inductance / permeabiltiy (two scales on the y axis)
    * formula for L as a function of permeability:
      * inducance for a cylinder
      * inductance with a core
    * then graphs of volume ration and permeability
    * graphs of mass ratio and permeability 
    
    
    
* Also talk about why the mass ratio graph appears how it does and what that means for the apperance of the volume ratio graph
* 

